Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-03-23 2017-Xudong-SMT/OpenPNets-SMT.tex
Add the description of interaction with Z3
In section 5, the description of input example and architecture. two graphs used.

%\begin{figure}[t]
%  \includegraphics[width=\linewidth]{XFIG/SMTLIB1}
%  \caption{The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
%\end{figure}

@@

\paragraph{Interaction with Z3}
\QIN{
\TODO{1. example input of Z3 in SMT-LIB 2. software architecture.}
}

\paragraph{translation of presentation}

@@

\TODO{
Xudong: full result of the tool execution on the running example\\\\
Open Automata of the CCS example.
}

>>>>

\begin{figure}[t]
  \centerline{\includegraphics[width=10cm]{XFIG/SMTLIB1}}
  \caption{The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
\end{figure}

@@

\paragraph{Interaction with Z3}
\TODO{1. example input of Z3 in SMT-LIB.[DONE] 2. software architecture.[DONE]}
\QIN{
We implement the dynamic interaction between the pNet API and Z3 solver through its JAVA API. But here we present the code in Z3 by SMT-LIB language instead of JAVA codes to make it easier to read. In Fig~\ref{schema:smt-lib}, we show the manual input of the unsatisfiable result before. Some $datatypes$ are declared to input the sorts of the CCS example, here we only declare one $datatypes$ named $Action$ to involve all the constant actions. The $Int$ and $Bool$ are already existed in Z3. Then we input the predicate of that open transition in two parts. The variables contained in the predicate are declared first, then the terms of predicate are inputed as $assertions$ one by one. In the output, "(not and)" shows Z3 have found out the contradiction in the predicate and the result "unsat" is just what we expected.  
}

\QIN{
We present the architecture of the interaction with Z3 in Fig~\ref{schema:interaction}. Both two parts need to be translated before submitting to the Z3. The $presentation$ of the pNet is declared at the beginning of the algorithm as the $sorts$ and the $operators$ will be used throughout the whole algorithm. It is translated into $datatypes$ and $functions$ then submitted to the Z3 at the same time. The predicate will be translated into $assertions$ before submitted to Z3 after the algorithm computing out all the possible open transitions, they act as intermediate results there. Together with the $datatypes$ and $functions$, the $assertions$ are used to check the satisfiability of the predicate in Z3.
}

\paragraph{translation of presentation}
\QIN{
The $datatypes$ are declared according to the $sorts$ the users declared in the $presentation$. Although in Fig~\ref{schema:smt-lib} we have not declared $functions$, they will be required if there are new $operators$ declared in the $presentation$. If the return type of the functions is one of the $datatypes$, we add this $function$ when declare the $datatypes$, it present the reality that every action expression also belongs to a sort of pNet. 
}

@@

\subsection{Result of the running example}
\TODO{
Xudong: full result of the tool execution on the running example\\\\
Open Automata of the CCS example.
}
